\documentclass[jou]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
  \ifthenelse{\equal{\string jou}{\string man}}{%
   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
  }{}%



% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}


\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Moving Beyond Academic Echo Chambers of Structural Equation Modeling: A Commentary on Hershberger (2003)},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines


% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}



\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{Moving Beyond Academic Echo Chambers of Structural Equation Modeling: A
Commentary on Hershberger (2003)}



  \author{Chi-Lin Yu\textsuperscript{1}}

  % \def\affdep{{""}}%
  % \def\affcity{{""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Department of Psychology, National Taiwan University  }

  \authornote{
    The present commentary is a homework (HW1) of Structural Equation
    Modeling course in Department of Psychology, National Taiwan University.
    Mentor: Li-Jen Weng. Student ID: R05227101 (Chi-Lin Yu). E-mail address:
    \href{mailto:r05227101@ntu.edu.tw}{\nolinkurl{r05227101@ntu.edu.tw}};
    \href{mailto:psychilinyu@gmail.com}{\nolinkurl{psychilinyu@gmail.com}}.
  }


  




\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}



Structural equation modeling (SEM) is a widely used statistical
procedure in psychological research. Over the past decades, SEM
applications are applied to numerous research, including both
substantive articles that adopted SEM to analyze real data and the
technical one that developed new progress of SEM. Nowadays, interests in
SEM is still high and continue to grow (Bollen \& Pearl, 2013). Here,
the present study reviewed the work done by Hershberger (2003), which
examined the growth of SEM from 1994 to 2001, to get a deeper
understandings of the SEM progress in the literature. In addition,
several own perspectives about the paper (Hershberger, 2003) and SEM
methodology itself are provided. The rest of the present paper is
organized as a quick review for Hershberger (2003), followed by a series
of proposed viewpoints and ends with a conclusion section.

\hypertarget{the-review}{%
\section{The Review}\label{the-review}}

Hershberger (2003) investigated the growth of SEM from 1994 to 2001.
They used \emph{PsycIFO} database to locate journal articles published
during these seven years. Both substantive and technical research with
SEM techniques were identified. Also, they specifically examine the
presence of SEM papers in American Psychological Association (APA)
journals. Likewise, the development of a SEM-specific journal,
\emph{Structural Equation Modeling: A Multidisciplinary Journal}, during
this period was studied. The results showed that the number of SEM
articles, both the number of substantive articles and the number of
technical articles, increased during this period. The technical articles
that published in \emph{Structural Equation Modeling: A
Multidisciplinary Journal} contributed as much as all other journals
combined. Forty-seven technical categories were created to characterize
the development of SEM methodology. SEM was also identified to have the
most consistently high level of development relative to other
multivariate statistical tools, such as exploratory factor analysis.
Overall, Hershberger (2003) suggested that SEM not only could be
considered as the most popular tool for multivariate method of data
analysis, but also had a stable methodological development with pace of
the use in practical research.

\hypertarget{the-encouraging-growth}{%
\section{The Encouraging Growth}\label{the-encouraging-growth}}

The most encouraging finding was that we could clearly see the progress
of SEM. The progress could be evidenced from four dimensions.

\setlength{\parindent}{4ex}

First of all, the number of SEM articles increased, which can be
obviously supported from the calculations in Hershberger (2003). During
these seven years, the number of substantive articles increased from 148
to 335, and the number of technical articles increased from 18 to 46.

Second, the number of technical subjects was expanded from 13 in 1994 to
almost 30 in 2001, suggesting the interests in SEM techniques become
more and more diverse. Although some fundamental topics were
consistently discussed in the literature, such as model specification
and goodness of fit, some novel but important topics were emerged then.
For example, the topic of scale invariance were first discussed in 1994
as Hershberger (2003) mentioned, and now this issue became really
popular in the recent years. Even the journal \emph{Chinese Journal of
Psychology} announced a special issue on related topics in 2018.

Third, the softwares for SEM also increased. Before 1974, the first
software package for SEM, \texttt{LISREL} (Joreskog \& Sorbom, 1996),
was developed. It is still one of the most widely used software packages
for SEM today. Some more popular commercial softwares, including
\texttt{EQS} (Bentler, 1995), \texttt{AMOS} (Arbuckle, 2011), and
\texttt{Mplus} (Muthén \& Muthén, 2010), were developed to support SEM
applications. With the advance of SEM methodology, several open source
tools were also designed to make all researchers have the possibility to
use and get better understandings of SEM. One of the most well known
example is \texttt{lavaan} (Rosseel, 2012), a free, open-source, and
high-quality package that has provided researchers a very good
alternative for latent variable modeling. The great number of citations
for all of the above-mentioned softwares also evidenced the development
of SEM.

Last but not least, since the emerge of SEM, its use has permeated
fields from psychology, business, education to even neuroimaging domain.
For example, a structural equation modeling approach for fMRI data (Kim,
Zhu, Chang, Bentler, \& Ernst, 2007) have been proposed in 2007,
allowing the explorations of effective connectivity maps with
event-related fMRI, and the development of SEM in neuroimaging domain is
still ongoing nowadays (Gates, Molenaar, Hillary, \& Slobounov, 2011).
The widely used of SEM in several different domains can strongly support
its popularity and continuous progress.

Overall, from these four dimensions, it was no doubt that there is an
active research community, and they have successfully promoted the
progress of SEM.

\hypertarget{the-rooms-for-improvements}{%
\section{The Rooms for Improvements}\label{the-rooms-for-improvements}}

\noindent Although the growth of SEM had been evidenced (Hershberger,
2003) and SEM as a great tool had provided better characterization of
data, it is equally important to let all SEM users understand its
technical progress and how to correctly use SEM/explain the results of
SEM.

\setlength{\parindent}{4ex}

Regarding the technical progress of SEM, most of these important
articles were published in \emph{Structural Equation Modeling: A
Multidisciplinary Journal}, and else were published in
methodology-specific journals, such as \emph{Psychometrika} and
\emph{Multivariate Behavioral Research}. Though the publications in
those specific journals can provided important contributions to SEM, it
is also clear that applied users without strong methodological
background will not be interested in those journals. Those applied
researchers are more likely to directly use SEM rather than
understanding its technical details. Thus, the latest SEM progress can
not be easily promoted and adopted in practical research.

In addition, despite the widespread use of SEM, misunderstandings
regarding its purpose and methods persist. In 2013, a chapter entitled
\enquote{Eight Myths About Causality and Structural Equation Models}
(Bollen \& Pearl, 2013) presented the eight misunderstandings of SEM.
Those myths contains all key procedures of SEM from the purpose (e.g.,
causal relations), the model, to the interpretations. It seems that user
and researchers (even reviewers), who used SEM to establish their
theories or tell their stories, do need a lot more training on SEM in
order to overcome the misinformation.

Perhaps one of the direct solutions to the aforementioned issues is to
publish papers in applied journals (e.g., \emph{ Psychological Science})
rather than only in methodological journals (e.g., \emph{Structural
Equation Modeling: A Multidisciplinary Journal}). Publish a paper in a
more general journal can elicit more discussion and make more people to
understand the issue. I used an article in fMRI domain as an example. An
article described some methodological issues in fRMI raised lot of
discussions in 2016 (Eklund, Nichols, \& Knutsson, 2016), further
allowing fMRI researchers to somehow reconsider their analyses. It is
clear that the effect will not blow up if they choose to publish their
article in a methodology-specific journal \emph{Neuroinformatics} rather
than a general journal \emph{Proceedings of the National Academy of
Sciences}. Of course, the impact factor and equality of these two
example journals are not the same, but I just want to point out that a
general journal may also be a good place to spread the methodological
ideas.

Some may argue that those general journals do not accept methodological
papers, and applied users still do not want to understand technical
details. I speculate that the commentary section in those journals might
be a possible place. That is, the main methodological details can be
presented in methodology-specific journals, and also send a brief
articles that includes all the important parts (i.e., guideline for new
method, suggestions..etc) as a commentary to general journals. Users can
first get a quick impression of the new progress of SEM and realize how
to apply those progress to their ongoing studies, and then users who
want to get a better understanding can read through the full paper with
methodological details.

In order to prevent SEM from becoming a widely used but poorly
understood statistical procedure, it is important to improve the
communication between methodologists and users. With successful
interaction between methodologists and users, not only SEM methodology
can have stable development with pace of the widespread use in practical
research, the future use of SEM in practical research can also catch up
with the progress of SEM methodology.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\noindent The present commentary reviewed the findings in Hershberger
(2003) and provided own viewpoints. Four dimensions for the growth of
SEM were discussed. Most of all, the rooms for improvements were also
suggested. The present study sincerely hopes that SEM community can move
beyond academic echo chambers, further expanding the energy and all
novel usages of SEM to all researchers.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-arbuckle2011ibm}{}%
Arbuckle, J. (2011). IBM spss amos 20 user's guide: IBM corporation.

\leavevmode\hypertarget{ref-bentler1995eqs}{}%
Bentler, P. M. (1995). \emph{EQS structural equations program manual}.
Multivariate software.

\leavevmode\hypertarget{ref-bollen2013eight}{}%
Bollen, K. A., \& Pearl, J. (2013). Eight myths about causality and
structural equation models. In \emph{Handbook of causal analysis for
social research} (pp. 301--328). Springer.

\leavevmode\hypertarget{ref-eklund2016cluster}{}%
Eklund, A., Nichols, T. E., \& Knutsson, H. (2016). Cluster failure: Why
fMRI inferences for spatial extent have inflated false-positive rates.
\emph{Proceedings of the National Academy of Sciences}, \emph{113}(28),
7900--7905.

\leavevmode\hypertarget{ref-gates2011extended}{}%
Gates, K. M., Molenaar, P. C., Hillary, F. G., \& Slobounov, S. (2011).
Extended unified sem approach for modeling event-related fMRI data.
\emph{NeuroImage}, \emph{54}(2), 1151--1158.

\leavevmode\hypertarget{ref-hershberger2003growth}{}%
Hershberger, S. L. (2003). The growth of structural equation modeling:
1994-2001. \emph{Structural Equation Modeling}, \emph{10}(1), 35--46.

\leavevmode\hypertarget{ref-joreskog1996lisrel}{}%
Joreskog, K., \& Sorbom, D. (1996). LISREL 8: User's reference guide
(scientific software international, chicago). \emph{Google Scholar}.

\leavevmode\hypertarget{ref-kim2007unified}{}%
Kim, J., Zhu, W., Chang, L., Bentler, P. M., \& Ernst, T. (2007).
Unified structural equation modeling approach for the analysis of
multisubject, multivariate functional mri data. \emph{Human Brain
Mapping}, \emph{28}(2), 85--93.

\leavevmode\hypertarget{ref-muthen2010mplus}{}%
Muthén, L. K., \& Muthén, B. O. (2010). \emph{Mplus: Statistical
analysis with latent variables: User's guide}. Muthén \& Muthén Los
Angeles.

\leavevmode\hypertarget{ref-rosseel2012lavaan}{}%
Rosseel, Y. (2012). Lavaan: An r package for structural equation
modeling and more. Version 0.5--12 (beta). \emph{Journal of Statistical
Software}, \emph{48}(2), 1--36.






\end{document}
