---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```
\setcounter{MaxMatrixCols}{20}

$\begin{bmatrix}
    \eta_{1} \\
    \eta_{2} \\
    \vdots \\
    \eta_{m} \\
    x_{1} \\
    x_{2} \\
    \vdots \\
    x_{p} \\
    y_{1} \\
    y_{2} \\
    \vdots \\
    y_{q}
\end{bmatrix}$
= 
$\begin{bmatrix}
    \beta_{11} & \beta_{12} & \dots & \beta_{1m} & 0_{11} & 0_{12} & \dots & 0_{1p} & 0_{11} & 0_{12} & \dots & 0_{1q} \\
    \beta_{21} & \beta_{22} & \dots & \beta_{2m} & 0_{21} & 0_{22} & \dots & 0_{2p} & 0_{21} & 0_{22} & \dots & 0_{2q} \\
    \vdots &  \vdots  &  \ddots &  \vdots  & \vdots & \vdots & \ddots & \vdots &\vdots &\vdots & \ddots & \vdots  \\
    \beta_{m1} & \beta_{m2} & \dots & \beta_{mm} & 0_{m1} & 0_{m2} & \dots & 0_{mp} & 0_{m1} & 0_{m2} & \dots & 0_{mq} \\
    0_{11} & 0_{12} & \dots & 0_{1m} & 0_{11} & 0_{12} & \dots & 0_{1p} & 0_{11} & 0_{22} & \dots & 0_{1q} \\
    0_{21} & 0_{22} & \dots & 0_{2m} & 0_{21} & 0_{22} & \dots & 0_{2p} & 0_{21} & 0_{22} & \dots & 0_{2q} \\
     \vdots &  \vdots  &  \ddots &  \vdots  & \vdots & \vdots & \ddots & \vdots &\vdots &\vdots & \ddots & \vdots  \\
    0_{p1} & 0_{p2} & \dots & 0_{pm} & 0_{p1} & 0_{p2} & \dots & 0_{pp} & 0_{11} & 0_{22} & \dots & 0_{pq} \\
    \lambda_{y11} & \lambda_{y12} & \dots & \lambda_{y1m} & 0_{11} & 0_{12} & \dots & 0_{1p} & 0_{11} & 0_{22} & \dots & 0_{1q} \\
    \lambda_{y21} & \lambda_{y22} & \dots & \lambda_{y2m} & 0_{21} & 0_{22} & \dots & 0_{2p} & 0_{21} & 0_{22} & \dots & 0_{2q} \\
     \vdots &  \vdots  &  \ddots &  \vdots  & \vdots & \vdots & \ddots & \vdots &\vdots &\vdots & \ddots & \vdots  \\
    \lambda_{yq1} & \lambda_{yq2} & \dots & \lambda_{yqm} & 0_{q1} & 0_{q2} & \dots & 0_{qp} & 0_{q1} & 0_{q2} & \dots & 0_{qq} \\
\end{bmatrix}$
$\begin{bmatrix}
    \eta_{1} \\
    \eta_{2} \\
    \vdots \\
    \eta_{m} \\
    x_{1} \\
    x_{2} \\
    \vdots \\
    x_{p} \\
    y_{1} \\
    y_{2} \\
    \vdots \\
    y_{q}
\end{bmatrix}$
$+$
$\begin{bmatrix}
    \gamma_{11} & \gamma_{12} & \dots & \gamma_{1n} & 1 & 0_{12} & \dots & 0_{1m} & 0_{11} & 0_{12} & \dots & 0_{1p} & 0_{11} & 0_{12} & \dots & 0_{1q} \\
    \gamma_{21} & \gamma_{22} & \dots & \gamma_{2n} & 0_{21} & 1 & \dots & 0_{2m} & 0_{21} & 0_{22} & \dots & 0_{2p} & 0_{21} & 0_{22} & \dots & 0_{2q} \\
    \vdots &  \vdots  &  \ddots &  \vdots  & \vdots & \vdots & \ddots & \vdots &\vdots &\vdots & \ddots & \vdots &\vdots &\vdots & \ddots & \vdots  \\
    \gamma_{m1} & \gamma_{m2} & \dots & \gamma_{mn} & 0_{m1} & 0_{m2} & \dots & 1 & 0_{m1} & 0_{m2} & \dots & 0_{mq} & 0_{m1} & 0_{m2} & \dots & 0_{mq} \\
    \lambda_{x11} & \lambda_{x12} & \dots & \lambda_{x1n} & 0_{11} & 0_{12} & \dots & 0_{1m} & 1 & 0_{22} & \dots & 0_{1p} & 0_{11} & 0_{12} & \dots & 0_{1q}\\
    \lambda_{x21} & \lambda_{x22} & \dots & \lambda_{x2n} & 0_{21} & 0_{22} & \dots & 0_{2m} & 0_{21} & 1 & \dots & 0_{2p} & 0_{21} & 0_{22} & \dots & 0_{2q}\\
     \vdots &  \vdots  &  \ddots &  \vdots  & \vdots & \vdots & \ddots & \vdots &\vdots &\vdots & \ddots & \vdots  \\
    \lambda_{xp1} & \lambda_{xp2} & \dots & \lambda_{xpn} & 0_{p1} & 0_{p2} & \dots & 0_{pm} & 0_{p1} & 0_{p2} & \dots & 1  & 0_{p1} & 0_{p2} & \dots & 0_{pq}\\
    0_{11} & 0_{12} & \dots & 0_{1n} & 0_{11} & 0_{12} & \dots & 0_{1m} & 0_{11} & 0_{12} & \dots & 0_{1p} & 1 & 0_{22} & \dots & 0_{1q} \\
    0_{21} & 0_{22} & \dots & 0_{2n} & 0_{21} & 0_{22} & \dots & 0_{2m} & 0_{21} & 0_{22} & \dots & 0_{2p} & 0_{21} & 1 & \dots & 0_{1q}\\
     \vdots &  \vdots  &  \ddots &  \vdots  & \vdots & \vdots & \ddots & \vdots &\vdots &\vdots & \ddots & \vdots &\vdots &\vdots & \ddots & \vdots \\
    0_{q1} & 0_{q2} & \dots & 0_{qn} & 0_{q1} & 0_{q2} & \dots & 0_{qm} & 0_{q1} & 0_{q2} & \dots & 0_{qp} & 0_{q1} & 0_{q2} & \dots & 1 \\
\end{bmatrix}$
$\begin{bmatrix}
    \xi_{1} \\
    \xi_{2} \\
    \vdots \\
    \xi_{n} \\
    \zeta{1} \\
    \zeta{2} \\
    \vdots \\
    \zeta{m} \\
    \delta{1} \\
    \delta{2} \\
    \vdots \\
    \delta{p} \\
    \epsilon{1} \\
    \epsilon{2} \\
    \vdots \\
    \epsilon{q}
\end{bmatrix}$

$\begin{bmatrix}
    \eta_{m \times 1} \\
    X_{p \times 1} \\
    Y_{q \times 1} \\
\end{bmatrix}$
=
$\left[
\begin{array}{c|c|c}
B_{m \times m} & 0_{m \times p} & 0_{m \times q}\\
\hline
0_{p \times m} & 0_{p \times p} & 0_{p \times q}\\
\hline
\Lambda_{y_{q \times m}} & 0_{q \times p} & 0_{q \times q} 
\end{array}
\right]$
$\begin{bmatrix}
    \eta_{m \times 1} \\
    X_{p \times 1} \\
    Y_{q \times 1} \\
\end{bmatrix}$
$+$
$\left[
\begin{array}{c|c|c|c}
\Gamma_{m \times n} & I_{m \times m} & 0_{m \times p} & 0_{m \times q}\\
\hline
\Lambda_{x_{p \times n}} & 0_{p \times m} & I_{p \times p} & 0_{p \times q}\\
\hline
0_{q \times n} & 0_{q \times m} & 0_{q \times p} & I_{q \times q}\\
\end{array}
\right]$
$\begin{bmatrix}
    \xi_{n \times 1} \\
    \zeta_{m \times 1} \\
    \delta_{p \times 1} \\
    \epsilon_{q \times 1} \\
\end{bmatrix}$

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
